### 2021-03-14 HW-Gravity/gravity1/gravity1.tex
Update gravity homework: add einbein solution

>>>>

\section{Einbein Action}
	The einbein action of a point particle is given by:
	\begin{equation}
		S[\eta,X] = \frac{1}{2} \int \dd{\tau} \pqty{
				\eta^{-1} \dot{X}_\mu \dot{X}^\mu
				- \eta m^2
			}
	\end{equation}
	Under worldline reparametrization: $\tau \mapsto \tau' = f(\tau)$, we have $X'(\tau') = X(\tau)$, i.e.~$X^\mu$ transforms like a \textbf{scalar} under worldline diffeomorphism; $
		X(\tau)
		\mapsto X'(\tau)
		= X\pqty{f^{-1}(\tau)}
	$.

	On the other hand, $\eta$ should be treated like an einbein: $\eta = \sqrt{-\gamma}$, here $\gamma = \gamma_{\tau\tau}$ is the worldline metric; $\gamma < 0$ due to the Lorentzian signature. We have:
	\begin{gather}
		\eta = \sqrt{-\gamma}
		\longmapsto \eta' = \eta\,
			\det \pdv{\tau}{\tau'}
		= \eta \pdv{\tau}{\tau'},
	\\[1ex]
		\eta^{-1}
		= - \sqrt{-\gamma}\,\gamma^{-1}
		\longmapsto (\eta')^{-1} = \eta^{-1}
			\pqty{\pdv{\tau}{\tau'}}
			\pqty{
				\pdv{\tau'}{\tau}
				\pdv{\tau'}{\tau}
			}
		= \eta^{-1} \pdv{\tau'}{\tau}
	\end{gather}
	It is clear that the action is invariant under the transformation:
	\begin{equation}
	\begin{aligned}
		S'
		&= \frac{1}{2} \int \dd{\tau'} \pqty\Big{
				(\eta')^{-1}
					\pdd{\tau'} X_\mu
					\pdd{\tau'} X^\mu
				- (\eta') m^2
			} \\
		&= \frac{1}{2} \int \dd{\tau}
			\pdv{\tau'}{\tau}\,
			\pqty{
				\eta^{-1}
					\pdv{\tau'}{\tau}
					\cdot
					\pdv{\tau}{\tau'}
					\pdd{\tau} X_\mu
					\cdot
					\pdv{\tau}{\tau'}
					\pdd{\tau} X^\mu
				- \eta\,\pdv{\tau}{\tau'}\,m^2
			} = S
	\end{aligned}
	\end{equation}

	We can eliminate $\eta$ classically by placing it on shell:
	\begin{equation}
		0 = \fdv{S}{\eta}
		= - \eta^{-2} \dot{X}_\mu \dot{X}^\mu
			- m^2,
	\quad
		\eta[X] = \frac{1}{m}
			\sqrt{-\dot{X}_\mu \dot{X}^\mu}
	\end{equation}
	Substitute this back to the action, and we have:
	\begin{equation}
	\begin{aligned}
		S[X] = S[\eta = \eta[X], X]
		&= \frac{1}{2} \int \dd{\tau} \pqty{
				m\,(
					-\dot{X}_\mu \dot{X}^\mu
				)^{-\frac{1}{2}}
				\dot{X}_\mu \dot{X}^\mu
				- m\,(
					-\dot{X}_\mu \dot{X}^\mu
				)^{+\frac{1}{2}}
			} \\
		&= -m \int \dd{\tau}
			\sqrt{-\dot{X}_\mu \dot{X}^\mu}
	\end{aligned}
	\end{equation}

\section{Ricci Tensor for Static Spherical Metric}
	Consider the metric:
	\begin{equation}
	\begin{aligned}
		\dd{s}^2
		= - f(r) \dd{t}^2
			+ h(r) \dd{r}^2
			+ r^2 \pqty{
				\dd{\theta}^2
				+ \sin^2\theta \dd{\phi}^2
			}
		= \eta_{ab}\, e^a e^b
	\end{aligned}
	\end{equation}
	Here we've defined the following vierbein:
	\begin{equation}
	\begin{aligned}
		e^t &= \sqrt{f(r)} \dd{t} \\
		e^r &= \sqrt{h(r)} \dd{r} \\
		e^\theta &= r \dd{\theta} \\
		e^\phi   &= r \sin\theta \dd{\phi} \\
	\end{aligned}
	\end{equation}
